### 2017-07-20 src/5_3_Proposal.tex
model updates before pseudoalgorithms

@@

\noindent so that VECM parameters $\mathbf{X}(t)$ are found using the following
equation:

\begin{equation}
\mathbf{B}(t) = \mathbf{A}(t) \mathbf{X}(t) + \mathbf{E}(t)\\
\end{equation}

The RR solution $\mathbf{\hat{X}}(t)$ using the sliding window matrices defined above
is:

@@

>>>>

\begin{equation}
\mathbf{B}(t) = \mathbf{A}(t) \mathbf{X}(t) + \mathbf{E}(t)\\
\label{eq:vareqt}
\end{equation}

\noindent where,

@@

The RR solution $\mathbf{\hat{X}}(t)$ of equation \ref{eq:vareqt} using the
sliding window matrices defined above is:

@@

\noindent here $\lambda$ corresponds to the regularization parameter (see section
\ref{sec:regularization}). When $\lambda=0$, the solution is equivalent to OLS.

The AAR solution only differs in the calculation $\mathbf{S}(t)$ which is
updated with the last input received $\mathbf{a}_{L+1}$:

\begin{equation}
\mathbf{S}(t) =
\sum_{i=0}^{L+1} \mathbf{a}_{t-i}\mathbf{a}_{t-i}^\top + \lambda \mathbb{I}
\label{eq:SAAR}
\end{equation}
